Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-18 article.Rmd
Remove static image
Make charts wider and more consistent

@@

ahr_proportions %>%
  ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Authors of Books Reviewed in the AHR by Gender") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  scale_fill_discrete(labels = c("Female", "Male", "Unknown")) +
  article_theme
```

@@

![Gap between female authorship of dissertations and books](img/book-dissertation-gap.jpg)

@@

combined_proportions %>%
  filter(gender != "unknown_proportion") %>%
  ggplot(aes(x = year, y = proportion, color = gender, size = type)) + 
  geom_line() +
  short_scale +
  scale_size_discrete(name = "Type",
                      labels = c("Book", "Dissertation"), range = c(2,1)) +
  scale_color_discrete(name = "Gender",
                       labels = c("Female", "Male")) +
  xlab(NULL) + ylab("Proportion of authors by gender") +
  ggtitle("The gap between between authorship of dissertations and books reviewed in the AHR ")
```

>>>>

knitr::opts_chunk$set(fig.width = 8, fig.height = 5)

@@

ahr_proportions %>%
  ggplot(aes(x = year, y = proportion, fill = gender)) + 
  geom_bar(binwidth = 1, stat = "identity") +
  ggtitle("Authors of Books Reviewed in the AHR by Gender") +
  xlab(NULL) + ylab(NULL) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0.5) +
  scale_fill_discrete(labels = c("Female", "Male", "Unknown")) +
  article_theme
```

@@

@@

combined_proportions %>%
  filter(gender != "unknown_proportion") %>%
  ggplot(aes(x = year, y = proportion, color = gender, size = type)) + 
  geom_line() +
  short_scale +
  geom_hline(yintercept = 0.5) +
  scale_size_discrete(name = "Type",
                      labels = c("Book", "Dissertation"), range = c(2,1)) +
  scale_color_discrete(name = "Gender",
                       labels = c("Female", "Male")) +
  xlab(NULL) + ylab("Proportion of authors by gender") +
  ggtitle("The gap between the genders of book and dissertation authors")
```
